Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-06-13 paper/paper.Rmd
3d = space + time

Two visualization types are supported: a two-dimensional and a three-dimensional method which can be selected via the logical argument `plot3d`.
The 3D visualization has been implemented via \pkg{plotly}.
Because a dynamic image cannot be included in this manuscript, a static version, which can be generated by setting `static_image = TRUE`, is shown.

@@

<!-- only some methods are suited for repeated execution -->
<!-- spcv_coords: limited variance due to limited k-means possibilties -->
For repeated executions of method `spcv_coords`, the variance between repetitions could be quite small due to the limited possibilities of different `k-means` clusters on the same dataset.
This applies even more to `"spcv_block"` with options `selection = "systematic"` and `selection = "checkerboard"` as the fold assignments are the same in each repetition.
Only methods with a random component (e.g. `"spcv_coords"` or `"spcv_block"` with option `selction = "random"`) may be suited for using multiple repetitions.

@@

We believe that making resampling methods available to widely used modeling frameworks is more benefitial than implementing such methods standalone in an R package.
The latter often require special structured objects as inputs and cannot directly be re-used in susequent modeling steps of user workflows.
This is not an issue specific to spatiotemporal resampling methods but a general philosophy of the authors.

>>>>

Two visualization types are supported: a two-dimensional and a three-dimensional method which can be selected via the logical argument `plot3d`.
The 3D visualization (space + time) has been implemented via \pkg{plotly}.
Because a dynamic image cannot be included in this manuscript, a static version, which can be generated by setting `static_image = TRUE`, is shown.

@@

<!-- only some methods are suited for repeated execution -->
<!-- spcv_coords: limited variance due to limited k-means possibilities -->
For repeated executions of method `spcv_coords`, the variance between repetitions could be quite small due to the limited possibilities of different `k-means` clusters on the same dataset.
This applies even more to `"spcv_block"` with options `selection = "systematic"` and `selection = "checkerboard"` as the fold assignments are the same in each repetition.
Only methods with a random component (e.g. `"spcv_coords"` or `"spcv_block"` with option `selction = "random"`) may be suited for using multiple repetitions.

@@

We believe that making resampling methods available to widely used modeling frameworks is more beneficial than implementing such methods standalone in an R package.
The latter often require special structured objects as inputs and cannot directly be re-used in subsequent modeling steps of user workflows.
This is not an issue specific to spatiotemporal resampling methods but a general philosophy of the authors.
